---
title: "On the origin of citation"
author: "PYT"
date: "September 15, 2015"
output:
  html_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    highlight: espresso
    number_sections: yes
    self_contained: no
    theme: cerulean
    toc: yes
---

# Load the data

```{r load_data}
counts_raw <- read.delim("data/counts-raw.txt.gz")
count_norm <- read.delim("data/counts-norm.txt.gz")
```

# Data exploration
What's the distribution of authors in all articles of our data set?
```{r author_histogram, fig.cap="Figure 1: Number of Authors per Article", echo=FALSE}
hist(counts_raw$authorsCount, main = "Authors per paper", xlab = "# author")
```

What's the distribution of facebook share in all articles of our data set?
```{r author_histogram_fb, fig.cap="Figure 2: Number of Facebook share per Article", echo=FALSE}
hist(counts_raw$facebookShareCount, main = "Facebook share per paper", xlab = "# shares")
```

The average number of Facebook shares per paper in the data set is `r mean(counts_raw$facebookShareCount)`.


## dplyr

```{r dplyr}
library(dplyr)
```

```{r}
research <- filter(counts_raw, articleType == "Research Article")
research_2006 <- filter(research, year == 2006)
research_2006_fb <- filter(research, year == 2006, facebookCommentCount > 0)
research_2006_fb_tweet <- filter(research, year == 2006, facebookCommentCount > 0 | backtweetsCount > 0, grepl("Infectious Diseases", plosSubjectTags))
```

```{r}
colnames(research)
article_info <- select(research, doi: authorsCount)
metrics <- select(research, contains("Count"), -authorsCount, f1000Factor, wikipediaCites)
```

```{r}
head(select(research, 3))
slice(article_info, 1:3)
```

```{r}
paper_2009 <- filter(counts_raw, year == 2009)
dim(paper_2009)
paper_2009_ft <- filter(paper_2009, facebookCommentCount > 1 | backtweetsCount > 1)
dim(paper_2009_ft)
paper_2009_ft_m <- filter(paper_2009_ft, mendeleyReadersCount > 1)
dim(paper_2009_ft_m)

low_site <- filter(research, year < 2009, pdfDownloadsCount > 1000, mendeleyReadersCount > 15, wosCountThru2011 < 10)
dim(low_site)
```

```{r}
facebook_2006 <- research %>% filter(year == 2006) %>% select(contains("facebook"))
head(facebook_2006)

research %>% filter(year == 2006) %>% select(contains("facebook")) %>% nrow
```

arrange, works similar to function order

```{r}
research %>% arrange(desc(authorsCount, wosCountThru2011)) %>% select(authorsCount, wosCountThru2011) %>% slice(1:10)
```

```{r}
research %>% arrange(desc(wosCountThru2011)) %>% select(title) %>% slice(1:3)

research %>% arrange(desc(authorsCount)) %>% select(authorsCount, title, journal, plosSubjectTags) %>% slice(1:3)
```

mutate
```{r}
research <- research %>% mutate(weeksSincePublished = daysSincePublished / 7, yearsSincePublished = weeksSincePublished / 52 )

research %>% select(contains("since")) %>% slice(1:10)
```

using summarize
```{r}
research %>% summarize(plot_mean = mean(plosCommentCount), plot_sd = sd(plosCommentCount), num = n())
```

using group_by
```{r}
research %>% group_by(journal, year) %>% summarize(tweet_mean = mean(backtweetsCount))

tweets_per_journal <- research %>% group_by(journal) %>% summarize(total = n(), tweet_mean = mean(backtweetsCount), SEM = sd(backtweetsCount)/sqrt(total))
```

## ggplot2

```{r}
library(ggplot2)
ggplot(research, aes (x = daysSincePublished, y = wosCountThru2011)) + geom_point(aes(color= journal), alpha = 0.1) + geom_smooth(color="red")
```

using scale
```{r}
p <- ggplot(research, aes (x = pdfDownloadsCount, y = wosCountThru2011)) + geom_point(aes(color= journal), alpha = 0.5) + geom_smooth()
p + scale_x_log10() + scale_y_log10()

ggplot(research, aes (x = log(pdfDownloadsCount + 1), y = log(wosCountThru2011+1))) + geom_point(aes(color= journal), alpha = 0.5) + geom_smooth() + scale_x_continuous(breaks = c(1, 3), labels = c(10, 100))


P + scale_color_grey()

library("RColorBrewer")
display.brewer.all()

p + scale_color_brewer(palette = "paired", labels = 1:7)

q <- ggplot(research, aes (x = sqrt(pdfDownloadsCount), y = sqrt(wosCountThru2011))) + geom_point(aes(color= journal), alpha = 0.5) + geom_smooth() + scale_color_brewer(palette = "Accent")

q + facet_wrap( ~journal)

research <- mutate(research, immuno = grepl("Immunology", plosSubjectTags))
ggplot(research, aes (x = sqrt(pdfDownloadsCount), y = sqrt(wosCountThru2011))) + geom_point(aes(color= journal), alpha = 0.5) + geom_smooth() + scale_color_brewer(palette = "Accent") + facet_grid(immuno ~journal)


tweets_bar <- ggplot(tweets_per_journal, aes(x = journal, y = tweet_mean)) +
  geom_bar(stat = "identity")
tweets_bar + geom_errorbar(aes(ymin = tweet_mean - SEM, ymax = tweet_mean + SEM), width= 0.1) + geom_text(aes(label = total, hjust = 0, vjust = 0))

tweets_per_journal_c <- research %>% group_by(journal, year) %>% summarize(total = n(), tweet_mean = mean(backtweetsCount), SEM = sd(backtweetsCount)/sqrt(total))

ggplot(tweets_per_journal_c, aes(x = journal, y = tweet_mean)) + geom_bar(stat = "identity") + geom_errorbar(aes(ymin = tweet_mean - SEM, ymax = tweet_mean + SEM), width= 0.1) + geom_text(aes(label = total, hjust = 0, vjust = 0)) + facet_wrap(~ year)

ggplot(research, aes(x = ))
```

